\documentclass[a4paper, 12pt]{article}
\usepackage[cm]{fullpage}

\usepackage{hyperref}
\hypersetup{
    pdftitle={My Resume},
    pdfauthor={Mikhail Rusakovich},
    pdfcreator={Mikhail Rusakovich},
    colorlinks=true,
    urlcolor=blue
}

\newcommand{\position}[1]{
    % bold
    \textbf{#1}}
\newcommand{\itemlabel}[1]{
    % italic + ":"
    \textit{#1:}}
\newcommand{\lastmodified}{
    \tiny{\itemlabel{Last Modified} \today}}

% Write current page number and Last Modified date in the footer
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % remove header line
\cfoot{\thepage}
\rfoot{\lastmodified}

\title{Mikhail Rusakovich}
\author{}
\date{}

\begin{document}
\maketitle

Highly motivated person with 3 years experience in software development with broad experience in working with Java-based tools and frameworks on different platforms.
Mostly experienced in developing of full stack enterprise- and web- applications.
Also I always have a great passion for learning new technologies, algorithms and really enjoy all kinds of open-source stuff.

\subsubsection*{Contacts:}
\begin{itemize}
    \item Tel: \href{tel:+375291798417}{+375 29 1798417}
    \item Email: \href{mailto:mikhail.complete@gmail.com}{mikhail.complete@gmail.com}
    \item Skype: \href{callto:mikhail.complete}{mikhail.complete}
    \item My legal name: Mikhail Rusakovich
\end{itemize}


\section*{Skills}

    \begin{itemize}
        \item Java, Groovy, C, PL/SQL (Oracle dialect, inc. query optimization, hierarchical queries), JavaEE (JSF, EJB, JPA, Servlets, JSP, JAX-WS, JAX-RS, JNDI, JMS, CDI), JAXB, JCE, Spring, GWT, Hibernate, ActiveMQ, Apache CXF, JavaFX, Swing, Applets, JUnit, Mockito, Arquillian
        \item Object Oriented Analysis and Design, GOF-Patterns, Multithreading
        \item \itemlabel{Web basic} HTTP, TCP/IP, HTML/CSS, Ajax, JavaScript, jQuery
        \item \itemlabel{Application and web containers} Weblogic, JBoss (WildFly), Tomcat, Glassfish
        \item \itemlabel{Specifications} XML, XSD, XSLT
        \item \itemlabel{Tools} Jenkins CI, Sonatype Nexus, Jira, SoapUI, Wireshark, SVN, Git, Maven, Ant, NSIS installation system
        \item \itemlabel{Strong knowledge} digital signature, security providers, CSP architecture, PKCS7 and CMS formats, certificates, CRL
    \end{itemize}


\section*{Work experience}

    \begin{itemize}

   
        \item \position{Java Developer}, Sep 2012--Jul 2013, Dec 2014 - present

            Developing and support TOPBY.by B2B EDI message provider which includes numerous conversion and connecting modules between customers located throughout the country.

            Also taking part in architecture development.
            	
            \begin{itemize}
                \item \itemlabel{Company} SoftClub, Minsk, Belarus
                \item \itemlabel{Responsibilities} Developing, testing, external system researching, profiling, debugging, reporting, integration with external systems
                \item \itemlabel{Tools \& technologies used} Java, C, JavaScript, JNI, Weblogic, Tomcat, Arquillian, ActiveMQ, Apache CXF, Spring, Groovy, JPA, JDBC, JAXB, XML, XSD, XSLT, Applets, Swing, JavaFX, Maven, SVN, Jira, Nexus, NSIS Scriptable Install System
            \end{itemize}
            
            \textbf{What was made:}
			\begin{itemize}
  				\item set application server's domain for high-load message processing
  				\item developed scalable message processing application based on a legacy code 
				\item deployed digital signature infrastructure, which includes supporting multiple security providers on the client and server side
  				\item integration with multiple partners using SOAP, REST, JMS
  				\item implemented numerous conversion modules from internal customer format to EANCOM and back
  				\item developed document generation system based on organization's templates
  				\item embedded SSF-security module for SAP system
			\end{itemize}
            
        \item \position{Java Developer}, Jan 2014--Dec 2014

           Homecredit Bank Belarus ibank retail. Internet banking for individuals. 

            \begin{itemize}
                \item \itemlabel{Company} SoftClub, Minsk, Belarus
                \item \itemlabel{Responsibilities} Frontend and backend developing, debugging, bug fixing, testing, reporting
                \item \itemlabel{Tools \& technologies used} Java, JSF (ICEfaces), JSP, EJB, Hibernate, JBoss, Dozer, Ant, jQuery, prototype.js, SVN, Jira
            \end{itemize}


        \item \position{Java Developer}, Jul 2013--Jan 2014

            BUTB.by Belarusian Universal Commodity Exchange. Exchange trading system.

            \begin{itemize}
                \item \itemlabel{Company} SoftClub, Minsk, Belarus
                \item \itemlabel{Responsibilities} Backend and service developing, testing, reporting, integration with external systems
                \item \itemlabel{Tools \& technologies used} Java, EJB, JPA, Servlets, Glassfish, Oracle PL/SQL, SOAP, Velocity, XDocReport, Ant, SVN, Jira
            \end{itemize}

    \end{itemize}    
    
\section*{Own open source projects}  

  
    \begin{itemize}
   
        \item \href{https://bitbucket.org/mikhail_complete/smarthome/src}{https://bitbucket.org/mikhail\_complete/smarthome}

            SmartHouse project is an attempt to create a universal platform for the management of home devices using popular interface interaction. At the moment, you can work with devices on the serial, USB and 1-wire protocols, and survey your real estate using a large number of supported cameras. To add support for the device is quite easy - you just need to add it in one of the configuration files. Also, some kinds of mock-devices are available for development stage.
            For complex logic devices control a special expression language was developed

            From ideas development to realization.

            \begin{itemize}
                \item \itemlabel{Tools \& technologies used} Java, C, GWT, Jetty, Spring, RMI, JNI, Bootstrap, JQuery, WebSocket, Maven, JUnit, Mockito, Cucumber, Selenium WebDriver, Git
            \end{itemize}

        \item \href{https://github.com/creepid/DocsReporter}{https://github.com/creepid/DocsReporter}

            Documents reporting system in docx, odt, pdf, xhtml and pptx formats extending XDocReport project and using Spring Framework.
Supported template formats: .docx, .odt and .pptx

            \begin{itemize}
                \item \itemlabel{Tools \& technologies used} Java, Spring, Velocity, Freemarker, JUnit, Mockito, Maven, Git
            \end{itemize}
            
    \end{itemize}    

\section*{Education}

    \begin{itemize}

        \item \position{Belarusian State University}, 2008--2013

            Diploma in Researching Physics.

    \end{itemize}

\section*{Appendix}

    \begin{itemize}
        \item \href{https://github.com/creepid}{https://github.com/creepid}
    \end{itemize}
        \begin{itemize}
        \item \href{https://bitbucket.org/mikhail_complete}{https://bitbucket.org/mikhail\_complete}
    \end{itemize}

\end{document}
