\documentclass[a4paper, 12pt]{article}
\usepackage[cm]{fullpage}

\usepackage{hyperref}
\hypersetup{
    pdftitle={CV},
    pdfauthor={Mikhail Rusakovich},
    pdfcreator={Mikhail Rusakovich},
    colorlinks=true,
    urlcolor=blue
}

\newcommand{\position}[1]{
    % bold
    \textbf{#1}}
\newcommand{\itemlabel}[1]{
    % italic + ":"
    \textit{#1:}}
\newcommand{\lastmodified}{
    \tiny{\itemlabel{Last Modified} \today}}

% Write current page number and Last Modified date in the footer
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % remove header line
\cfoot{\thepage}
\rfoot{\lastmodified}

\title{Mikhail Rusakovich}
\author{}
\date{}

\begin{document}
\maketitle

\subsubsection*{Contacts:}
\begin{itemize}
	\item Current location: CIS, Belarus, Minsk
    \item Tel: \href{tel:+375291798417}{+375291798417}
    \item Email: \href{mailto:rusakovichma@gmail.com}{rusakovichma@gmail.com}
    \item LinkedIn: \href{https://linkedin.com/in/rusakovichma
}{https://linkedin.com/in/rusakovichma}
\end{itemize}

My experience includes working as a Software Engineer in Security for 6 years and as a Senior Security Advisor for the last 3 years. 
\newline
\newline
My mission I see in building an effective, scalable and continuous application security program, evangelism the security between development teams, and closing all the gaps from a security perspective in the requirement, design and implementation phases around projects and the whole Company.
\newline
\newline
I also have the experience in coordinating an Application Security team. 
\newline
\newline
Available for relocation and ready to work remotely.


\section*{Last Work Experience}

    \begin{itemize}
        \item \position{EPAM Systems, Inc. (Dec 2018 - Jul 2021, 2 years 8 months)}, Senior Application Security Engineer;
        \newline
        \newline
            \textbf{Responsibilities:}
			\begin{itemize}
				\item Continuous Company products Security Assessment;
  				\item Threat Modeling and Risk Assessment toolset design and implementation;
  				\item Increasing Company Secure SDLC program maturity with new practices and activities; 
  				\item Development of Security Maturity framework for the Company products;
  				\item Company Security Tools (SAST/DAST/WAF) extensions and plugins development;
  				\item Company projects portfolio Security Reference Architecture and Identity \& Access management practices;
  				 \item Support Security Champions program with new Trainings, demonstrations and guidelines development.
  				\newline
  				\newline
			\end{itemize}
    \end{itemize} 
            
    \begin{itemize}
        \item \position{SoftClub LLC, (Aug 2012 - Dec 2018, 6 years 5 months)}, Lead Software Software in Security, FinTech and Trade sector products;
        \newline
        \newline
            \textbf{Responsibilities:}
			\begin{itemize}
				\item Initiation of Security program for the Company products;
  				\item Development, architecting and Security Analysis of Public Key Infrastructure (PKI) services and clients applications for Banking and Trade sector;
  				\item Engineering and support of Electronic Data Interchange (EDI) Provider back-end services for Trade sector;
				\item Back-end business- and security- services (authentication, authorization, signing, audit operations, etc.) development for Trade sector.
			\end{itemize}
    \end{itemize}
    
\section*{Education}

    \begin{itemize}

        \item \position{Belarusian State University}, 2008--2013, Researcher Bachelor Degree.
            \newline\textbf{Degree work on a theme:} 
            \newline "Software Development for EPR spectrometer management"
    \end{itemize}
    

\section*{Certifications \& Educational programs}

    \begin{itemize}
        \item CSSLP (Certified Secure Software Lifecycle Professional)
        \item PCI Professional (PCIP)™ Qualification certification
        \item Amazon Web Services (AWS) Security and Identity \& Access Management.
    \end{itemize}
    

\section*{Other information}  
Apart from my work, I love to participate in conferences and open-source projects (especially security-related), try to share with the world \href{https://github.com/EasyAppSecurity}{my own solutions on github} and share my experience \href{https://mikhailrusakovich.wordpress.com/}{via blog}. Please, request additional details about my experience via one of the suggested methods above in case of any questions.


    
\section*{Languages}
 	\begin{itemize}
 		 \item \position{English} - Professional level.
 		 \item \position{Russian} - Native.

 	\end{itemize}    
    
\end{document}
